\paragraph{To Prof. Ron Milo}
For opening the door to the fascinating world of biology to me.
For your constant pursue of perfection and simplicity.
For teaching me how science should be done and guiding me in learning the fundamentals of scientific work.
For your patience, support, and uncompromising commitment to excellence.
For promoting science that focuses on addressing burning issues humanity faces.
\paragraph{To the Milo lab members at present and in the past}
An extraordinary cadre of talented and committed people who have always provided good advice, and were willing to support me in my research at all times, helping me take it into higher levels.
Who create a great atmosphere to be part of, and who, by their complementing skills and expertise, highlight the power of cooperation and mutual exchange of ideas in doing science.
\paragraph{To the Weizmann Institute of Science and the Feinberg Graduate School}
That support innovative research by creating an amazing environment focused on facilitating productive scientific research and interaction.
Maintaining a welcoming, green and vast campus, where one can wander in search of ideas and meditate.
For avoiding unnecessary bureaucracies and providing unusual flexibility, demonstrating the institute's spirit of commitment to scientific excellence.
\paragraph{And especially to Hilla, my wife}
For her endless support and encouragement, especially during harder periods of uncertainty, doubt, and frustration.
For being by my side throughout this journey.
