\documentclass[a4page,notitlepage]{article}
\input{preamble.tex}
\toggletrue{article}
\togglefalse{eddpathway}

\tikzset{
  invisible/.style={opacity=0},
  visible on/.style={}
}


\renewcommand\thesection{}
\renewcommand\thesubsection{}
\renewcommand\thesubsubsection{}
\title{Design principles of autocatalytic cycles constrain kinetic parameters and force over expression of enzymes at flux branch points}
\author{Uri Barenholz, Dan Davidi, Ed Reznik, Yinon Bar-On, Niv Antonovsky, Elad Noor, Ron Milo}
\date{}
\begin{document}
\input{varsdefs.tex}
\maketitle
\abstract{
    A system that requires the presence of a component in order to increase the amount of that component is an autocatalytic cycle with respect to that component.
    Autocatalytic cycles are present in a wide range of domains, from the  chicken and egg metaphore, representing the essentiality of members of a spicies to exist in order to reproduce and increase the number of members of the spicies, through the essentiality of components of the central dogma such as DNA and ribosomes in order for a cell to multiply, thus increasing the amount of these components, all the way to the essentiality of specific substrates in metabolic networks to enable synthesis of excess amounts of those substrates, such as the essentiallity of ATP in glycolysis, for the synthesis of excess amounts of ATP.
    Autocatalytic cycles present unique features with specific implications in the context of metabolic networks.
    We show, by systematic search, that most reactions in central carbon metabolism either take part in metabolic autocatalytic cycles, or consume metabolites that are also intermediates of such cycles.
    Some of the autocatalytic cycles we identify are generally not considered as such.
    Using the most simple form of a metabolic autocatalytic cycle, we derive design principles necessary to enable stable fluxes through such a cycle.
    We show that the principles we find, constraining kinetic parameters and expression levels of participating enzymes, are also relevant in more general cases.
    The constraints we find are that, for stable fluxes through an autocatalytic cycle to occur, the autocatalytic reactions, recycling the metabolites of the cycle, must have higher affinity and lower maximal flux than the reactions consuming metabolites of the cycle to generate biomass.
    These findings imply that stability of autocatalytic cycles limits the affinity of enzymes in the metabolic network and forces excess expression of enzymes that catalyse the reactions consuming metabolites of the cycle.
    We test these constraints using existing experimental measurements in vivo and find them to hold for functioning autocatalytic cycles for which data is available.
    We discuss various extensions of the simple model including the effects of external fluxes into the cycle, showing how the metabolic network uses such constructs to possibly overcome the limitations we find.
    This work thus serves as an approachable introduction to the analysis of autocatalytic metabolic cycles, presenting the design principles they adhere to, and as a demonstration of the insights one can get by these principles on real networks, specifically explaining seemingly inefficient enzyme expression levels and low affinities.
}
\input{autocatalysis-content.tex}
\section{Acknowledgments}
We would like to thank Arren Bar-Even, Katja Tummler, Daniel Segre, Matthias Heinemann, David Fell, Patrick Shih, Noam Prywes, Leeat Keren, David Wernick, Wolfram Liebermeister, Rami Pugatch and \dots for fruitful discussions and valuable insights contributing to this work.
%(Acknowledge tikz/latex/pgf/xcolor/stackexchange community for supporting free software tools)
\bibliography{library}{}
\bibliographystyle{ieeetr}
\section{Supplementary Information}
\beginsupplement
\input{autocatalytic-supplementary.tex}
\end{document}
